\documentclass{article}

\begin{document}
\title{Using Bibliographies in \LaTeX}
\author{Dale Alleshouse}
\maketitle

% -------------------- Main document --------------------------------

\section{Introduction}
Using and managing bibliographies in \LaTeX\ is very easy. These are the steps required to use them:

Not this again, it's a \emph{tragedy}. What is its problem?  \verb|This is some funky verb texts|.

\begin{enumerate}
  \item Create a main document file
  \item Create a project
  \item Collect bibliography entries in a \verb|.bib| file. For this:
    \begin{itemize}
      \item Get the bibliography from Google Scholar/ACM or wherever (much easier) or
      \item Writes the entry yourself. I want one!
    \end{itemize}
  \item Add a \verb|\bibliographystyle| and a \verb|\bibliography| command to your document.
  \item \emph{Cite} the references where you need using the key.
  \item Build the project a couple of times to get the citations in the main document. This is an
    auspicious issue.
\end{enumerate}

\section{Some Background Text}
We are going to use this section to put some text in our document and at some points, we are going
to inset a reference. This, for example, is going to turn into a
reference~\cite{se-cs-collab:nauman10}. This~\cite{nauman2011using} is yet another reference. And so
on.\cite{seo2011user} I need to site my idol, Donald Knuth~\cite{knuth1997art}. What about one more
new in-cite-ful citation~\cite{seo2011user}.

Let's try this again\ldots.


% -------------------------------------------------------------------
% add bibliography-related commands here

\bibliographystyle{plain}
\bibliography{bibfile}

\end{document}
